SubsidyExplorer - Step 7: Pre-Populated Proposals

### 2022-08-15 scripts/07_proposals.Rmd
running all proposals including final agreement for summary figures and tables

# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.5

end_year <- 2080

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "_FINAL/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Proposal settings
#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
  dplyr::filter(include != "Hide")

@@

```{r}
  # A) global (aggregated) "kobe" final year plot
  box_2050_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = 2050,
                                            plot_name = "box_scenario_type_2050_plot",
                                            plot_width = 7.5,
                                            plot_height = 6,
                                            results_dir = results_dir,
                                            group_var = "run_group",
                                            color_var = "run_group",
                                            legend_pos_manual = "bottom",
                                            legend_name = "Scenario Type",
                                            plot_type = "box")

figure_5 <- cowplot::plot_grid(box_2050_plot, compare_2050_plot, ncol = 1, rel_heights = c(1,0.75), axis = "lr", align = "v", labels = c("(A)", "(B)"), hjust = -1)
ggsave(paste0(results_dir, "Fig5.tiff"), figure_5, width = 7.5, height = 8)

## Extract 2050 and end year results for all proposals and save as nice tables

@@

# Now make a pretty version for 2050 only
all_results_global_output_table_2050_pretty <- all_results_global_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 3),
         Catches = round(Catches*100, 3),
         Revenue = round(Revenue*100, 3),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 3))

@@

# Get rounded end values
global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

# Now do regional
all_results_regional_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Region, Category, order, Year) %>%
  dplyr::select(-order)

@@

# Now make a pretty version for 2050 only
all_results_regional_output_table_2050_pretty <- all_results_regional_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 3),
         Catches = round(Catches*100, 3),
         Revenue = round(Revenue*100, 3),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 3))

@@

## Do the same with aboslute values

```{r}
# all_results_global_absolute_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
#   summarize(BAU_tot = sum(BAU, na.rm = T),
#             Reform_tot = sum(Reform, na.rm = T),
#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
#                                      TRUE ~ 0)) %>%
#   ungroup() %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                               Variable == "catches_total" ~ "Catches")) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 abs_Diff_tot,
#                 Variable) %>%
#   spread(Variable, abs_Diff_tot)
# 
# write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))
# 
# all_results_regional_absolute_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                                 Variable == "catches_total" ~ "Catches")) %>%
#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
#                               TRUE ~ 0)) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 Region,
#                 abs_Diff,
#                 Variable) %>%
#   spread(Variable, abs_Diff)
# 
# write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
```

>>>>

# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.5
end_year <- 2080
folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_FINAL_AGREEMENT/")

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), folder_name)
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Proposal settings
#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
#   dplyr::filter(include != "Hide")
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL_AGREEMENT.csv"), stringsAsFactors = F) %>%
  dplyr::filter(include != "Hide")

@@

```{r}
if(make_plots){
  # A) global (aggregated) "kobe" final year plot
  box_2050_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = 2050,
                                            plot_name = "box_scenario_type_2050_plot",
                                            plot_width = 7.5,
                                            plot_height = 6,
                                            results_dir = results_dir,
                                            group_var = "run_group",
                                            color_var = "run_group",
                                            legend_pos_manual = "bottom",
                                            legend_name = "Scenario Type",
                                            plot_type = "box")

figure_5 <- cowplot::plot_grid(box_2050_plot, compare_2050_plot, ncol = 1, rel_heights = c(1,0.75), axis = "lr", align = "v", labels = c("(A)", "(B)"), hjust = -1)
ggsave(paste0(results_dir, "Fig5.tiff"), figure_5, width = 7.5, height = 8)
}
```
## Extract 2050 and end year results for all proposals and save as nice tables

@@

# Now make a pretty version for 2050 only
all_results_global_output_table_2050_pretty <- all_results_global_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))

@@

# Get rounded end values for the most ambitious scenario
global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
```

```{r}
# Now do regional
all_results_regional_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Region, Category, order, Year) %>%
  dplyr::select(-order)

@@

# Now make a pretty version for 2050 only
all_results_regional_output_table_2050_pretty <- all_results_regional_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))

@@

## Do the same with absolute values

```{r}
# # We want these to be ordered by date within each category, so we need to go back to our list
# date_order <- proposal_settings %>%
#   dplyr::select(title_tool, date) %>%
#   rownames_to_column("order") %>%
#   mutate(order = as.numeric(order))

# Collect global results
all_results_global_output_table_absolute <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot - BAU_tot,
                            TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Diff_tot_absolute = Diff_tot,
                Variable) %>%
  spread(Variable, Diff_tot_absolute) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Category, order, Year) %>%
  dplyr::select(-order)

write.csv(all_results_global_output_table_absolute, paste0(results_dir, "all_results_global_output_table_absolute.csv"))

# write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))
# 
# all_results_regional_absolute_table <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                                 Variable == "catches_total" ~ "Catches")) %>%
#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
#                               TRUE ~ 0)) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 Region,
#                 abs_Diff,
#                 Variable) %>%
#   spread(Variable, abs_Diff)
# 
# write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
```
